Thermal performance of fish is explained by an interplay between physiology, behaviour, and ecology

### 2019-01-31 Cons_physio_revision.tex
revised submission

Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\citealt{deutsch_climate_2015,pinsky_marine_2013}). As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\citealt{deutsch_climate_2015, stuart-smith_thermal_2015, parmesan_globally_2003, walther_ecological_2002}).  \hl{Such predictions of changes in species ecology based on physiological function are important to ensure appropriate policy and management response to changing environments and expected effects on organisms}\cite{mckenzieconservation2016, pattersonperspective2016}. However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems. Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\citealt{brander_overconfidence_2013, lefevre_models_2017}). In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\citealt{cheung_shrinking_2013}). \hl{Such changes in fish growth and size would have downstream implications for fisheries stock assessment (e.g., by changing population productivity) and management tools such as size limits}. However, these predictions have been criticized as overly simplistic and not in line with physiological constraints (\citealt{brander_overconfidence_2013, lefevre_models_2017}).

@@

Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\citealt{glazier_activity_2009,brett_1965_relation}, and the activity fraction. Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \citealt{jeschke_predator_2002, sentis_parsing_2013}) and approximated by an Arrhenius scaling $c(T) = e^{E_a(T-T_0)/(b\cdot T\cdot T_0)}$ \cite{gilloolyeffects2001}, where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (such that c(T)=1 at 15\degree C), and $b$ is the Boltzmann constant. Note that we only scale rates related to enzymatic activity with temperature, we do not assume that ecological rates such as foraging rates or activity are a direct function of temperature. Rather, they are modulated by an individual's behavioural response to temperature driven physiological changes.

The oxygen budget $P_{0_2}(w,T)$ (or aerobic scope) follows a similar form to the mass budget:
\begin{align}
  P_{0_2}(w,T) &= S_{O_2}(w,T) - D_{O_2}(w,T) \\
        &= S_{O_2}(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
\end{align}
Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for all metabolic processes in Eq.~\ref{eq:P} (except assimilation losses), with $\omega$ being amount of oxygen required per mass.  The oxygen supply ($S_{O_2}(w,T)$) scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as a MOS that increase continuously up to a lethal temperature (fig.~\ref{fig:O2_fig_used}). The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and corresponds to the maximum metabolic rate (MMR) in our model. Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\citealt{priede_metabolic_1985}). \hl{ In our model, MMR and maximum oxygen supply are equivalent as we do not explicitly model contributions from anaerobic metabolism, such as during burst swimming or hypoxia. During such events, the actual metabolic rate may be higher than oxygen consumption alone would suggest, however such states cannot usually be sustained (and therefore fall outside of the sustained MMR defined here).} We assume that oxygen supply is temperature dependent and follows a flexible dome-shaped function (\citealt{gnauck_2013_freshwater, lefrancois_influence_2003}):

@@

\hl{ Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the second term in $S_{O_2}(T)$ term describes the dependence on ambient $O_2$ concentrations at temperature $T$ ($O_2(T)$).} At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function \cite[e.g.,][]{lefrancois_influence_2003}. \hl{We specify $C_{O_2}^{\text{50}}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $C_{O_2}^{\text{crit}}$ is the ambient concentration at which oxygen supply ceases. Ambient oxygen concentration levels are assumed to decline with temperature according to a curve that approximates declines of dissolved oxygen in saltwater at 35 PSU as $l\cdot e^{-0.01851*(T-5)}$, with $l$ the oxygen concentration at 5\degree C.} To specify $\lambda(T)$, we define $T_{\text{max}}$ as the lethal temperature for the species, and $T_{\text{opt}}$ as the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height. Note that we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (fig.~\ref{fig:O2_fig_used}).

@@

\item Growth curves predicted through ontogeny, which allow us to compare growth performance early and late in life (i.e., juvenile growth vs asymptotic size).
\item Production efficiency, here defined as available energy for both growth and reproduction, relative to the food consumption (i.e., $\frac{P(w,T)}{f(w,T)h c(T) w^q)}$.
\item The dimensionless ratio of $\frac{P}{Mw}$, which is analogous to the short-sighted fitness aproximation (Gilliam's rule) used above.
\item Fitness integrated over an individual's lifetime, defined as $R_0$ (see below).

@@

Fitness consequences for particular life-history strategies (trait combinations, see below) at different temperatures can be investigated if one considers the time-scales in the model to be short relative to evolutionary time-scales (i.e., if the model represents ecological time-scales). On these time-scales, we assume that adaptive responses are negligible \cite[see, however, ][]{moffett_local_2018, sandblom_plastic_2016}. We investigate over-all fitness with respect to temperature by calculating $R_0$, the lifetime reproductive output, for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here. $R_0$ is the appropriate measure of fitness when density dependence mainly operates early in life \cite{kozlowskican2004}, as is often assumed for fish \cite{andersenwhen2017, lorenzendensity2018}, and was calculated as

@@

Increasing metabolic demands at higher temperatures leads to increased activity levels in order to optimise energy gains relative to mortality risk (fig.~\ref{fig:activity}). This difference in activity level is especially pronounced in slow strategy species, for which the over-all activity level is markedly lower and which consistently show higher activity over all sizes for the simulated life-history (fig.~\ref{fig:size-act}). A similarly higher activity lelve is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.~\ref{fig:size-act}). For these individuals, the higher activity levels and metabolic demands lead to an active metabolic rate that is close to their MMR. For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig.~\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature. For species with a rising MOS with temperature, oxygen is not limiting (fig.~\ref{fig:activity-rising}). However, larger fast strategy individuals are predicted to show a slightly dome-shaped relationship between activity levels and temperature at intermediate sizes, and slightly decreasing activity levels in response to temperature at large sizes, despite available aerobic scope for activity. \hl{This adjustment is a function of metabolic activity costs assumed here - if we assume smaller metabolic costs for activity, activity levels are always higher at higher temperature} (fig.~\ref{fig:size-act_low}).

Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig.~\ref{fig:feeding}). For slow strategy species, higher activity levels at warmer tmeperatures lead to relatively stable feeding levels, but a substantially higher mortality coupled with slightly increased available energy leads to an over-all decline in the ratio of $P$ to $M$. Available energy shows a dome-shaped response to temperature in slow strategists, and is maximised at relatively high temperatures. However, it is limited by oxygen availability only at high temperatures in species with a dome-shaped MOS. Production efficiency follows a near opposite trend due to the relatively flat response in the feeding level $f$, but temperature driven increases in maximum consumption.

@@

The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\citealt{cheung_shrinking_2013, pauly_sound_2017}). We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\citealt{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models \cite[e.g., ][]{guiet_effects_2016} and species specific eco-physiology models (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}). In addition, our model provides a more explicit, physiology-based mechanistic model to derive general predictions about temperature effects on ectotherms than previous general frameworks such as the OCLTT. Predictions from the OCLTT are both contributing to patterns in fitness and ecological rates shown here, but are also only part of the picture, and we suggest that future improvements of predictive frameworks should center on model critisism and improvements, and leave behind semantic discussions about conceptual constructs that are difficult to explicitly link to data. \hl{Improved eco-physiological models will provide a more robust basis for incorporating eco-physiology into tactical management and strategic conservation planning} \cite{mckenzieconservation2016, pattersonperspective2016}.

@@

 The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper.

@@

\bibliographystyle{amnatnat}
\begin{thebibliography}{55}
\linespread{1.5}
\providecommand{\natexlab}[1]{#1}

@@

@@

\begin{figure}[!ht]
{\centering 
\includegraphics[width=\maxwidth]{figure/norms-1} 
}
\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth. Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f). Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms}
\end{figure}

\begin{figure}[!ht]
{\centering 
\includegraphics[width=\maxwidth]{figure/infs-1} 
}
\caption[Interactive effects of food availibility and temperature on the asymptotic size ($L_{\infty}$), with increasing linewidth showing increasing food resource availibility for a) slow and b) fast life-history species]{Interactive effects of food availibility and temperature of the asymptotic size ($L_{\infty}$), with increasing linewidth showing increasing food resource availibility for a) slow and b) fast life-history species.}\label{fig:infs}
\end{figure}

\begin{figure}[!ht]
{\centering 
\includegraphics[width=0.8\maxwidth]{figure/fit-1} 
}
\caption[Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)]{Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (a) and fast strategy (b) species at the assumed maturation-raction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing linewidth, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing linewidth)}\label{fig:fit}
\end{figure}

@@

\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\begin{figure}[!ht]
\centering
\includegraphics[width=\maxwidth]{figure/activitys-1} 
\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; aandb) and fast strategy (fast life-history; c, d).}
\label{fig:activity-rising}
\end{figure}

@@

\begin{figure}[!ht]
{\centering 
\includegraphics[width=\maxwidth]{figure/norms_neg-1} 
}
\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth. Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f). Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_neg}
\end{figure}

\begin{figure}[!ht]
{\centering 
\includegraphics[width=\maxwidth]{figure/norms_pos-1} 
}
\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth. Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availibility from top (a/b) to bottom (e/f). Baseline resource availibility assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_pos}
\end{figure}

>>>>

Temperature, through its effects on individual physiology, is a dominant driver of species ecology and bio-geography (\citealt{deutsch_climate_2015,pinsky_marine_2013}). As a consequence, current and predicted temperature increases under climate change will act as a strong agent of change in many ecosystems (\citealt{deutsch_climate_2015, stuart-smith_thermal_2015, parmesan_globally_2003, walther_ecological_2002}).  \hl{Such predictions of changes in species ecology based on physiological function are important to ensure appropriate policy and management response to changing environments and expected effects on organisms}(\citealt{mckenzieconservation2016, pattersonperspective2016}). However, the nature of these changes can be difficult to predict as temperature effects scale from individuals to species and ecosystems. Through this cascade of scales, incorrect or approximate model assumptions at the individual scale can have disproportionate effects on ecosystem level outcomes (\citealt{brander_overconfidence_2013, lefevre_models_2017}). In marine fish, for example, recent predictions of decreasing organism size, and resulting decreases in the size of fisheries catches (\citealt{cheung_shrinking_2013}). \hl{Such changes in fish growth and size would have downstream implications for fisheries stock assessment (e.g., by changing population productivity) and management tools such as size limits}. However, these predictions have been criticized as overly simplistic and not in line with physiological constraints (\citealt{brander_overconfidence_2013, lefevre_models_2017}).

@@

Metabolic demands ($D(w,T)$) are standard metabolism ($\propto k w^n$), which scales with exponent $n<1$, and active metabolism $\propto \tau k_a w$, which scales proportional to mass owing to muscular demands scaling approximately isometrically with weight (\citealt{glazier_activity_2009,brett_1965_relation}, and the activity fraction. Temperature scaling of metabolic rates (standard and active metabolism, and maximum consumption rate) is determined by enzymatic processes (e.g., digestion, glycolysis \citealt{jeschke_predator_2002, sentis_parsing_2013}) and approximated by an Arrhenius scaling $c(T) = e^{E_a(T-T_0)/(b\cdot T\cdot T_0)}$ (\citealt{gilloolyeffects2001}), where $E_a$ is the activation energy, assumed constant, $T_0$ is the reference temperature (such that c(T)=1 at 15\degree C), and $b$ is the Boltzmann constant. Note that we only scale rates related to enzymatic activity with temperature, we do not assume that ecological rates such as foraging rates or activity are a direct function of temperature. Rather, they are modulated by an individual's behavioural response to temperature driven physiological changes.

The oxygen budget $P_{0_2}(w,T)$ (or aerobic scope) follows a similar form to the mass budget:
\begin{align}
  P_{0_2}(w,T) &= S_{O_2}(w,T) - D_{O_2}(w,T) \\
        &= S_{O_2}(T) w^n - \omega c(T) \left( \beta f(w,T) h w^q + k w^n + k_a w \right).
\end{align}
Demand ($D_{O_2}(w,T)$) is the sum of oxygen used for all metabolic processes in Eq.~\ref{eq:P} (except assimilation losses), with $\omega$ being amount of oxygen required per mass.  The oxygen supply ($S_{O_2}(w,T)$) scales with body weight as $w^n$ multiplied by a flexible dome-shaped function that can emulate both a dome-shaped maximum oxygen supply (MOS) as well as a MOS that increase continuously up to a lethal temperature (fig.~\ref{fig:O2_fig_used}). The maximum oxygen consumption is the oxygen consumption during maximal activity level that can be sustained over some time, and corresponds to the maximum metabolic rate (MMR) in our model. Although the MMR is often used synonymously with both maximum oxygen supply and demand, in some species the maximal oxygen consumption ($D^{max}_{O_2}(T)$) is not reached at maximum activity levels, but rather during digestion (\citealt{priede_metabolic_1985}). \hl{ In our model, MMR and maximum oxygen supply are equivalent as we do not explicitly model contributions from anaerobic metabolism, such as during burst swimming or hypoxia. During such events, the actual metabolic rate may be higher than oxygen consumption alone would suggest, however such states cannot usually be sustained (and therefore fall outside of the sustained MMR defined here).} We assume that oxygen supply, \hl{taken as the aggregated process of oxygen delivery from diffusion across respiratory organ membranes (e.g., gills) to delivery for cellular metabolism,} is temperature dependent and follows a flexible dome-shaped function (\citealt{gnauck_2013_freshwater, lefrancois_influence_2003}):

@@

\hl{ Here $\lambda(T)$ specifies the temperature dependency of $O_2$ supply, whereas the second term in $S_{O_2}(T)$ term describes the dependence on ambient $O_2$ concentrations at temperature $T$ ($O_2(T)$).} At constant temperature $T$, oxygen supply is a function of ambient oxygen and is assumed to follow a saturating function \cite[e.g.,][]{lefrancois_influence_2003}. \hl{We specify $C_{O_2}^{\text{50}}$ as the point where oxygen supply has dropped by 50\% relative to the saturation level $\lambda(T)$, and $C_{O_2}^{\text{crit}}$ is the ambient concentration at which oxygen supply ceases. Ambient oxygen concentration levels are assumed to decline with temperature according to a curve that approximates declines of dissolved oxygen in saltwater at 35 PSU as $l\cdot e^{-0.01851*(T-5)}$, with $l$ the oxygen concentration at 5\degree C.} To specify $\lambda(T)$, we define $T_{\text{max}}$ as the lethal temperature for the species, and $T_{\text{opt}}$ as the temperature at which oxygen supply is maximised; $\eta$ determines the width of the dome-shape, and $\zeta$ its height. \hl{Note that the simulated increase in the aggregated oxygen supply includes potential increases in oxygen delivery via increased diffusive (passive) supply at higher temperatures} (\citealt{verberk_oxygen_2011}) \hl{as well as increased active delivery of oxygen made possible by increased heart rates at higher temperatures} \cite[e.g.,][]{lefrancois_influence_2003}. With the above formulation, we can emulate an oxygen supply (and hence maximum metabolic rate; MMR) that increases up to the lethal temperature by setting the temperature for maximum oxygen delivery close to the lethal temperature (fig.~\ref{fig:O2_fig_used}).

@@

\item Growth curves predicted through ontogeny, which allow us to compare growth performance early and late in life (i.e., juvenile growth vs asymptotic size).
\item Production efficiency, here defined as available energy for both growth and reproduction, relative to the food consumption (i.e., $\frac{P(w,T)}{f(w,T)h c(T) w^q)}$.
\item The dimensionless ratio of $\frac{P}{Mw}$, which is analogous to the short-sighted fitness approximation (Gilliam's rule) used above.
\item Fitness integrated over an individual's lifetime, defined as $R_0$ (see below).

@@

Fitness consequences for particular life-history strategies (trait combinations, see below) at different temperatures can be investigated if one considers the time-scales in the model to be short relative to evolutionary time-scales (i.e., if the model represents ecological time-scales). On these time-scales, we assume that adaptive responses are negligible \cite[see, however, ][]{moffett_local_2018, sandblom_plastic_2016}. We investigate over-all fitness with respect to temperature by calculating $R_0$, the lifetime reproductive output, for a given maturation-reaction norm and trait parameters - we thus do not consider evolutionary consequences of changes in fitness here. $R_0$ is the appropriate measure of fitness when density dependence mainly operates early in life (\citealt{kozlowskican2004}), as is often assumed for fish (\citealt{andersenwhen2017, lorenzendensity2018}), and was calculated as

@@

Increasing metabolic demands at higher temperatures leads to increased activity levels in order to optimise energy gains relative to mortality risk (fig.~\ref{fig:activity}). This difference in activity level is especially pronounced in slow strategy species, for which the over-all activity level is markedly lower and which consistently show higher activity over all sizes for the simulated life-history (fig.~\ref{fig:size-act}). A similarly higher activity level is observed for small fast strategy individuals (e.g., post-larval) for which even initial activity levels are very high (fig.~\ref{fig:size-act}). For these individuals, the higher activity levels and metabolic demands lead to an active metabolic rate that is close to their MMR. For all other sizes across the two trait scenarios, oxygen is only limiting to activity at the extremes of the simulated temperature range (fig.~\ref{fig:activity}), and only for species with a dome-shaped MOS with respect to temperature. For species with a rising MOS with temperature, oxygen is not limiting (fig.~\ref{fig:activity-rising}). However, larger fast strategy individuals are predicted to show a slightly dome-shaped relationship between activity levels and temperature at intermediate sizes, and slightly decreasing activity levels in response to temperature at large sizes, despite available aerobic scope for activity. \hl{This adjustment is a function of metabolic activity costs assumed here - if we assume smaller metabolic costs for activity, activity levels are always higher at higher temperature} (fig.~\ref{fig:size-act_low}).

Temperature and metabolic demand-driven adjustments to the activity level lead to substantial changes in performance related metrics in both trait scenarios (fig.~\ref{fig:feeding}). For slow strategy species, higher activity levels at warmer temperatures lead to relatively stable feeding levels, but a substantially higher mortality coupled with slightly increased available energy leads to an over-all decline in the ratio of $P$ to $M$. Available energy shows a dome-shaped response to temperature in slow strategists, and is maximised at relatively high temperatures. However, it is limited by oxygen availability only at high temperatures in species with a dome-shaped MOS. Production efficiency follows a near opposite trend due to the relatively flat response in the feeding level $f$, but temperature driven increases in maximum consumption.

@@

The importance of the interaction between ecology, bio-energetics and oxygen limitations in deriving realistic predictions about temperature impacts on ecological rates and fitness calls into question predictions for climate change impacts based on simple models of growth alone (\citealt{cheung_shrinking_2013, pauly_sound_2017}). We suggest that the general trait-based approach presented here provides a parsimonious compromise between simplistic approximations that may provide misleading predictions about future ecosystems (\citealt{brander_overconfidence_2013, lefevre_models_2017}), and more complex eco-physiological models such as dynamic energy budget models \cite[e.g., ][]{guiet_effects_2016} and species specific eco-physiology models (\citealt{hufnagl_physiological_2011, holt_climate_2014,holt_climate_2015}). In addition, our model provides a more explicit, physiology-based mechanistic model to derive general predictions about temperature effects on ectotherms than previous general frameworks such as the OCLTT. Predictions from the OCLTT are both contributing to patterns in fitness and ecological rates shown here, but are also only part of the picture, and we suggest that future improvements of predictive frameworks should center on model critisism and improvements, and leave behind semantic discussions about conceptual constructs that are difficult to explicitly link to data. \hl{Improved eco-physiological models will provide a more robust basis for incorporating eco-physiology into tactical management and strategic conservation planning} (\citealt{mckenzieconservation2016, pattersonperspective2016}).

@@

The authors would like to thank members of the DTU Centre for Ocean Life modeling group for stimulating discussions over the course of the development of the ideas in this paper. We also thank Christian Jørgensen and three anonymous reviewers, who provided helpful reviews that greatly clarified the manuscript.

@@

\bibliographystyle{amnatnat}
\begin{thebibliography}{62}
\linespread{1.5}
\providecommand{\natexlab}[1]{#1}

@@

\bibitem[{Verberk et~al.(2011)Verberk, Bilton, Calosi, and
  Spicer}]{verberk_oxygen_2011}
Verberk, W.~C., D.~T. Bilton, P.~Calosi, and J.~I. Spicer. 2011
\newblock Oxygen supply in aquatic ectotherms: partial pressure and solubility
  together explain biodiversity and size patterns 92:1565--1572.

@@

\begin{figure}[!ht]
{\centering 
\includegraphics[width=\maxwidth]{figure/norms-1} 
}
\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth. Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availability from top (a/b) to bottom (e/f). Baseline resource availability assumed in all other simulations is that shown in panels c and d.}\label{fig:norms}
\end{figure}

\begin{figure}[!ht]
{\centering 
\includegraphics[width=\maxwidth]{figure/infs-1} 
}
\caption[Interactive effects of food availability and temperature on the asymptotic size ($L_{\infty}$), with increasing line width showing increasing food resource availability for a) slow and b) fast life-history species]{Interactive effects of food availability and temperature of the asymptotic size ($L_{\infty}$), with increasing line width showing increasing food resource availability for a) slow and b) fast life-history species.}\label{fig:infs}
\end{figure}

\begin{figure}[!ht]
{\centering 
\includegraphics[width=0.8\maxwidth]{figure/fit-1} 
}
\caption[Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (left column) and fast strategy (right column) species at the assumed maturation-reaction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing line width, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing line width)]{Fitness ($R_0$), relative to maximum fitness within (a and b) oxygen limited (blue) and non-oxygen limited (teal) for slow- (left column) and fast strategy (right column) species at the assumed maturation-reaction norm and default parameters, and (c and d) changes in relative fitness with respect to temperature resulting from decreasing levels of activity cost symbolised by decreasing line width, and (e and f) changes in relative fitness with respect to temperature as a function of increasing food availability (increasing line width)}\label{fig:fit}
\end{figure}

@@

\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\begin{figure}[!ht]
\centering
\includegraphics[width=\maxwidth]{figure/activitys-1} 
\caption{Optimum (red long-dashed), maximum (green short-dashed) and realised (blue solid lines) activity levels (left column [a,c]) at increasing temperatures for a 10g fish with a continuously increasing MOS with increasing temperature, with corresponding oxygen demand (right column [b,d]); maximum oxygen supply (MOS; green short-dashed), standard metabolism (red long-dashed) and realised (active; blue solid lines) metabolic demand, as well as metabolic scope (orange long-dashed) at activity level $\tau$, for slow strategy (slow life history; a and b) and fast strategy (fast life-history; c, d).}
\label{fig:activity-rising}
\end{figure}

@@

\begin{figure}[!ht]
{\centering 
\includegraphics[width=\maxwidth]{figure/norms_neg-1} 
}
\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the negative reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth. Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availability from top (a/b) to bottom (e/f). Baseline resource availability assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_neg}
\end{figure}

\begin{figure}[!ht]
{\centering 
\includegraphics[width=\maxwidth]{figure/norms_pos-1} 
}
\caption[On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth]{On ecological time-scales, increasing temperature (purple to yellow growth curves) modifies growth, and maturation age changes according to the positive reaction norm (black dots at 50\% allocation to reproduction), whereas asymptotic size is affected by changes in absolute energy available for growth. Growth curves are shown for slow- (left column [a,c,e]) and fast strategists (right column [b,d,f]), at increasing food availability from top (a/b) to bottom (e/f). Baseline resource availability assumed in all other simulations is that shown in panels c and d.}\label{fig:norms_pos}
\end{figure}
